---
title: "Simple document"
output: github_document
---


```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

## Import some data

I want to import `FAS_litters.csv`


```{r}
litters_df = read_csv("data/FAS_litters.csv")
```

Imported dataset, rename now

```{r}
names(litters_df)

litters_df = janitor::clean_names(litters_df)
```

```{r}
litters_df

head(litters_df)
tail(litters_df)
```


view shows data in separate window in table form
```{r, eval = FALSE}
view(litters_df)
```


skimr shows brief summary
```{r}
skimr::skim(litters_df)
```

##ARguments in `read_csv`

```{r}
litters_df =
  read_csv(
    "data/FAS_litters.csv",
    skip = 5,
    col_names = FALSE,
    na = "Low8")
```



##Parsing Columns

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
```



##Reading from Excel

Reading MLB data

```{r}
mlb11_df = read_excel("data/mlb11.xlsx")
```


LotR Words 


```{r}
fellow_df = read_excel("data/LotR_Words.xlsx", range = "B3:D6")
```



## Read a SAS file

```{r, eval = FALSE}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")
```



I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.